### 2020-06-15 docs/LaTex/Paper.tex
Minor fixes

\section{Introduction}
This project arises itself from a direct interaction with professionals inside forestal sector. The original idea was to give technical coverage for particular necessities which professionals in this sector had to face off with. At this point is easy to notice this solution will need to be a distributed solution, due high samples dispersion. \lang{As can be seen}, there are even remote techniques to predict this sample density/dispersion using remote methods which predicts \doubt{between $157$-$170$ indviduals per hectare}\cite{ForestStandVol} (depending on the used model). So according to this and sample size determination theories, to get a great resolution could be necessary a big size for samples and the necessity of a big wireless network of distributed devices, since each device will correspond with an individual.

@@

It is important to note that \lang{when talking about \enquote{low-power consumption}, in many cases it is actually meaning} battery-powered devices, for example.

>>>>

\section{Introduction}
This project arises itself from a direct interaction with professionals inside forestal sector. The original idea was to give technical coverage for particular necessities which professionals in this sector had to face off with. At this point is easy to notice this solution will need to be a distributed solution, due high samples dispersion. As indicated, there are even remote techniques to predict this sample density/dispersion using remote methods which predicts \doubt{between $157$-$170$ indviduals per hectare}\cite{ForestStandVol} (depending on the used model). So according to this and sample size determination theories, to get a great resolution could be necessary a big size for samples and the necessity of a big wireless network of distributed devices, since each device will correspond with an individual.

@@

It is important to note that when talking about \enquote{low-power consumption}, in many cases it is actually meaning battery-powered devices, for example.
